{\it E}nKCF: Ensemble of Kernelized Correlation Filters for High-Speed, Object Tracking

### 2017-08-10 wacv_for_review.tex
Comments Replied

\textbf{Evaluation with Deep Features}Our focus so far was to build a high
speed tracker that can run about 30fps on a single-board, embedded
system. Given this goal, we used HoG and color features in an
efficient way for the proposed {\it E}nKCF. Deep Learning features, on
the other hand, recently have been proved to boost tracking accuracy
of some of the online tracking algorthms \cite{ma2015hierarchical,
  danelljan2015convolutional}. For this reason, we believe that, the
{\it E}nKCF tracker can perform better with deep learning features if
a target embedded system has GPUs.

@@

  I don't know why Figure 7 is presented separately from Figure 5. If
  you want to keep this way, you need, at least, to have their scales
  same -- precision should have the same range, say 0.8 as the max
  value.
}

For example, \cite{danelljan2015convolutional} used the activations of
the first and second convolutional layer features of the VGGNet
\cite{simonyan2014very} where their experiments showed that the first
convolutional layer features lead to slightly better precision and
success rates than the second layer. \cite{ma2015hierarchical}
proposed a KCF tracker with deeper features. Their method employs the
third convolutional layer features to get the response map. In the
next stage, they use the translation estimation from the first stage
to employ second convolutional layer features. Finally, the first
convolutional layer features is extracted from the position estimated
in the second stage. This coarse-to-fine position estimation approach
allows embedding more representative features of the object. However,
such approach requires multiple runs of a KCF at a single frame,
increasing the run-time complexity. For this reason, we follow a
similar approach to \cite{danelljan2015convolutional} to embed deep
learning features.

>>>>

\textbf{Evaluation with Deep Features} Our focus so far was to build a high
speed tracker that can run at 30fps on a single-board, embedded
system. Given this goal, we used HoG and color features in an
efficient way for the proposed {\it E}nKCF. Deep features, on
the other hand, recently have been proved to boost tracking accuracy
of the KCFs based trackers \cite{ma2015hierarchical,
  danelljan2015convolutional}. For this reason, we believe that, the
{\it E}nKCF tracker can perform better with deep features trained
on ImageNet dataset. Accomodating deep features on a single-board
system prohibits from tracking at targeted speed. However, with the
availability of GPUs on the embedded system, {\it E}nKCF tracker can
afford convolutional neural network features (CNN) to improve tracking
accuracy. Therefore, we wanted to evaluate how much accuracy gain we
can achieve by switching from hand-crafted features to CNN features.

@@

  I don't know why Figure 7 is presented separately from Figure 5. If
  you want to keep this way, you need, at least, to have their scales
  same -- precision should have the same range, say 0.8 as the max
  value.

  \it YoungWoo : The point of adding this section is to evaluate the
  same tracker with deep features (CNN) and see how much accuracy improvement
  we get. However, I tried to highlight that, by employing deep features
  the targeted embedded system changes from low-end (CPU-only) to 
  higher-end system (GPUs). The two papers I cited employs the features
  from the first several layers of the VGGNet. This is a common practice
  in supporting the trackers with CNN features. If I add this to figure 5,
  it does not make sense, because all the trackers we compare, use hand-crafted
  features and run on CPU. For this reason, I wanted to compare EnKCF 
  with deep features (higher-end system) and hand-crafted features (low-end system).

  The figure 7(a) and figure 5 have almost the same range (0,73 and 0.70)
  I will update the figure 5 to have 0.73 range as well. I test the EnKCF
  with CNN features only on the UAV123 dataset.
}

There has been numerous studies on applying a pretrained CNN features
to tracking-by-detection algorithms. For example, 
\cite{danelljan2015convolutional} used the activations of
the first and second convolutional layer features of the VGGNet
\cite{simonyan2014very} where their experiments showed that the first
convolutional layer features lead to slightly better precision and
success rates than the second layer. \cite{ma2015hierarchical}
proposed a KCF tracker with deeper features. Their method employs the
third convolutional layer features to get the response map. In the
next stage, they use the translation estimation from the first stage
to employ second convolutional layer features. Finally, the first
convolutional layer features is extracted from the position estimated
in the second stage. This coarse-to-fine position estimation approach
allows embedding more representative features of the object. However,
such approach requires multiple runs of a KCF at a single frame,
increasing the run-time complexity. For this reason, we follow a
similar approach to \cite{danelljan2015convolutional} to embed deep
learning features.
